%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{calc} % added
\usepackage{ragged2e}

\input{glyphtounicode}


%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    \begin{minipage}[t]{0.99\linewidth} % Adjust the width as needed
      {#1}
    \end{minipage}
    \vspace{1pt} % Adjust the space between elements as needed
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheadingLeftOneRow}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\newcommand{\resumeSubSubheadingLeftTwoRows}[4]{%
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
    \item[\small #3]{\textit{\small  #4}}
\end{description}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemSubListHeading}[1]{
  \vspace{-7pt}
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      {\small#1}
    \end{tabular*}\vspace{-7pt}
}
\newcommand{\resumeItemSubListStart}{\begin{itemize}[label=--]\vspace{3pt}}
\newcommand{\resumeItemSubListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

%-------------------------------------------

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Maksim Khvostov} \\ \vspace{1pt}
    \small +370-660-49-220 $|$ \href{mailto:mkliverout@gmail.com}{\underline{mkliverout@gmail.com}} $|$ 
    \href{https://linkedin.com/in/makentoshe}{\underline{linkedin.com/in/makentoshe}} $|$
    \href{https://github.com/Makentoshe}{\underline{github.com/Makentoshe}}
\end{center}

\vspace{5pt}\small{ I am interested in any programming problems and Android memory leaks. Self-motivated for any Kotlin, Android,
and IoT projects. Have deep experience in Jetpack Compose and retail projects, worked with Google Maps and
Google Play Services. Configured and supported CI/CD via TeamCity. }
\begin{itemize}[label=\hbox{\tiny$\bullet$}]\vspace{-5pt}
\item\small{ Have 3+ years of commercial experience.}\vspace{-5pt}
\item\small{ Have 3 years of mentoring and teaching experience. }\vspace{-5pt}
\item\small{ Have 5 years of Android development experience in general. }\vspace{-5pt}
\end{itemize}\vspace{-5pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{Oct. 2022 -- Present}
      {EPAM Systems - THAT Concept Store}{Remote, Lithuania}
      
      \resumeItemListStart
      
        \resumeItem{ 
          \resumeItemSubListHeading { Participation:  }
          \resumeItemSubListStart
            \resumeSubItem {Led multi-module support and Jetpack Compose integration}
	  \resumeSubItem {Supported unit tests for Jetpack Compose}
	  \resumeSubItem {Supported tooling for other developers}
	  \resumeSubItem {Interviewing new people for the project}
          \resumeItemSubListEnd
        }
	
        \resumeItem{
          \resumeItemSubListHeading{Achievements:}
          \resumeItemSubListStart
            \resumeSubItem{Implemented fast and expandable views that can be used in default Android views and in Compose views as well without any additional support}
            \resumeSubItem{Introduced some tweaks for a user interface to increase user experience and implemented them in the application}
            \resumeSubItem{Helped transfer the application to a multi-module structure /TODO: check build time}
            \resumeSubItem{Led application migration from default Android views to Jetpack Compose}
          \resumeItemSubListEnd
       }

        \resumeItem{
          \resumeItemSubListHeading{Team Composition:}
          \resumeItemSubListStart
            \resumeSubItem{Android Team: 4 members}
            \resumeSubItem{BA Team: 1 member}
            \resumeSubItem{QA Team: 2 members}
            \resumeSubItem{iOS Team: 4 members}
            \resumeSubItem{Backend Team: 4+ members}
          \resumeItemSubListEnd
        }
        
        \resumeItem{ \textbf{ Technologies:}  Kotlin, detekt, Dagger2, MVVM, Jetpack Compose }
      \resumeItemListEnd
     
      \resumeSubheading
      {Software Engineer}{Aug. 2022 -- Dec. 2022}
      {EPAM Systems - Animeal}{Remote, Lithuania}
      
      \resumeItemListStart
      
        \resumeItem{ 
          \resumeItemSubListHeading { Participation:  }
          \resumeItemSubListStart
            \resumeSubItem { Designed and implemented UI kit }
	  \resumeSubItem { Designed the project architecture }
	  \resumeSubItem { Introduced issues decomposition }
	  \resumeSubItem { Improved git flow processes }
          \resumeItemSubListEnd
        }
        
        \resumeItem{ \textbf{ Technologies:} Kotlin, Jetpack Compose, detekt, MapboxMaps, Dagger2 and Hilt, MVVM, gms }
      \resumeItemListEnd
      
      \resumeSubheading
        {Software Engineer}{Aug. 2021 -- Aug. 2022}
        {EPAM Systems - Beacons }{Hybrid, Saint-Petersburg}
      
      \resumeItemListStart
      
        \resumeItem{ 
          \resumeItemSubListHeading { Participation:  }
          \resumeItemSubListStart
            \resumeSubItem { Configured CI/CD pipelines, static analysis, and designed release processes for application, which
reduced the time between code review and task completion by 30\% }
	  \resumeSubItem {  Implemented the login screen with integrated SSO and improved SSL usage in the application }
	  \resumeSubItem { Supported for navigation and pathfinding functional }
	  \resumeSubItem { Migrated from Butterknife to ViewBinding library }
	  \resumeSubItem { Integrated a real-time monitoring system }
          \resumeItemSubListEnd
        }
        
        \resumeItem{ \textbf{ Technologies:} Android SDK, Kotlin, Java, Dagger2, Coroutines, Butterknife, ViewVinding, RxJava2,
WebView
 }
      \resumeItemListEnd
  
% jetBrains Academy - Hyperskill
    \resumeSubheading
      {Android Specialist (part time contract position)}{Nov. 2019 -- Dec. 2021}
      {JetBrains Academy (Hyperskill)}{Remote, Saint-Petersburg}
      
      \vspace{5pt}\small{ Was responsible for all projects in the Android track. Each project describes an android task challenge
          with several(3-7) steps on completion. Each step is covered with integration and unit tests.
          Created several projects myself, implemented templates and configured the build system for a quick
          development start.
          Providing full support for creating an Android course at Hyperskill }
      
      \resumeItemListStart
      
        \resumeItem{ 
          \resumeItemSubListHeading { Participation:  }
          \resumeItemSubListStart
            \resumeSubItem { Managed projects quality }
	  \resumeSubItem { Implemented a library for fast test writing }
          \resumeItemSubListEnd
        }
        
        \resumeItem{ \textbf{ Technologies:}  Kotlin, detekt, Dagger2, MVVM, Jetpack Compose }
      \resumeItemListEnd


    \resumeSubheading
      {Android Developer (Summer internship)}{Jul. 2020 -- Sep. 2020}
      {JetBrains (Space)}{Remote, Saint-Petersburg}
      
      \vspace{5pt}\small{ 
	Implemented an issue tracking screen for the JetBrains Space App. Also, provided a Proof-of-Concept
	for the Projects screen.
      }
      
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The Bonch-Bruevich Saint-Petersburg State University of Telecommunications}{2019 -- 2021}
      {Master's degree, Automation of Technological Processes and Facilities}{Saint-Petersburg, Russia}
    \resumeSubheading
      {The Bonch-Bruevich Saint-Petersburg State University of Telecommunications}{2015 -- 2019}
      {Bachelor's degree, Automation of Technological Processes and Facilities}{Saint-Petersburg, Russia}
  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Kotlin, C++} \\
     \textbf{Frameworks and Libraries}{: Jetpack Compose, Room, JUnit, Mockk, Mockito, Robolectric } \\
     \textbf{Databases}{: SQLite, MongoDB } \\
     \textbf{Architecture and Design}{: REST, MVI, MVVM } \\
     \textbf{Developer Tools}{: Gradle, Git, MAT } \\
     \textbf{CI/CD}{: GitLab CI/CD, Docker, TeamCity, AppCenter} \\
    }}
 \end{itemize}


%-----------LANGUAGES-----------
\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Intermediate (B2)} \\
     \textbf{Russian}{: Native}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}